Requirements and Current State of Knowledge Representation Systems for Service Robotics

### 2012-04-17 krs-survey.tex
Filled section on standard reasoning techniques

\newcommand{\ie}{{\textit{i.e.~}}}
\newcommand{\cf}{{\textit{cf~}}}
\newcommand{\eg}{{\textit{e.g.~}}}

@@

Backtracking,...

\paragraph{Decidability}

...

>>>>

\newcommand{\concept}[1]{{\footnotesize \texttt{#1}}}
\newcommand{\ie}{{\textit{i.e.~}}}
\newcommand{\cf}{{\textit{cf~}}}
\newcommand{\eg}{{\textit{e.g.~}}}

@@

Being based on logical languages to represent the knowledge, most of the
systems we survey allow various forms of \emph{reasoning}.

We call \emph{standard reasoning techniques} techniques based on logical
inference, using resolution algorithms like \emph{forward chaining},
\emph{backward chaining} or \emph{semantic tableaux}.

Main reasoning problems include \emph{concept satisfiability},
\emph{consistency checking} and \emph{instance checking}.

Concept satisfiability verifies if it is possible to find a non-empty
\emph{interpretation} of a concept (or an expression defining a concept) in the
knowledge model. For instance, the formula \concept{Plant} $\land$
\concept{isRed}, which defines the concept of red plants, is satisfiable in a
model \concept{KB} iff $\exists a, $ \concept{Plant}$(a) \land$
\concept{isRed}$(a)$, \ie if we can find at least one red plant $a$ in our
model.

Checking the consistency of a model is equivalent to checking the
satisfiability of each of the concept defined in the knowledge model.

Instance checking consists in verifying that an individual $a$ is an
interpretation of a concept (or concept expression) $C$ in the knowledge model.
A typical example would be that we are provided with an instance
\concept{object1} and we want to know if this object is a kind of
\concept{Bottle} or \concept{Glass}.

Reasoners can then provide other type of inferences, like:

\begin{itemize}
    \item class subsumption (similar to inheritance)

    \item reasoning on roles properties, including:
        \begin{itemize}
        \item entailments based on roles domain and range (for instance, if the
        domain of the role \concept{thinksOf} is known to be
        \concept{ThinkingAgent}, then \concept{thinksOf}$(a, b) \to
        $\concept{ThinkingAgent}$(a)$),

        \item universal, existantial and cardinality constraints (including \concept{allValue}, 
        \concept{someValue}, \concept{hasValue}),

        \item property characteristics (symmetry, transitivity, etc.)

    \item complex concept expressions like: \par \footnotesize \concept{Bottle}
    $\equiv$ \concept{Artifact} {\bf that} (\concept{hasShape} {\bf value}
    \concept{cylinderShape})\footnote{This example uses the \emph{Manchester
    syntax}, \url{http://www.w3.org/TR/owl2-manchester-syntax/}} \normalsize

    \item set operations like: \par \footnotesize \concept{Color} $\equiv$ {\bf
    unionOf}(\concept{blue}, \concept{green}, \concept{orange},
    \concept{black}...) \normalsize

\paragraph{Rule Languages}
\item generic SWRL ({\em Semantic Web Rule Language}) rules like: \par
        \footnotesize \concept{looksAt(?agt, ?obj)} $\land$
        \concept{pointsAt(?agt,?obj)} \par $\Rightarrow$ \concept{focusesOn(?agt, ?obj)}
        \normalsize
